On exponential sums arising from the classical doubling method

### 2025-03-20 paper.tex
Cleanup

		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{+}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$

@@

		The group $\GroupExtension{G}$ is isomorphic to the subgroup $\GSO^{-}_{2n}\left(\finiteField\right)$ of $\GL_{2n}\left(\finiteField\right)$, consisting of elements $g$ such that defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$

>>>>

		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{+}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{+}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} w_{2n} g = \lambda w_{2n},\,\, \det g = \lambda^n\right\}.$$

@@

		The group $\GroupExtension{G}$ is isomorphic to the group $\GSO^{-}_{2n}\left(\finiteField\right) \subset \GL_{2n}\left(\finiteField\right)$, defined as the projection to the first coordinate of the $\finiteField$-points of $$\algebraicGroup{\GSO}^{-}_{2n} = \left\{\left(g, \lambda\right) \in \algebraicGroup{\GL}_{2n} \times \multiplcativeScheme \mid \transpose{g} B_{n,d} g = \lambda B_{n,d},\,\, \det g = \lambda^n\right\}.$$
